MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Sparse Model

### 2020-03-25 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
add future pkg
add ENSEMBL mirror

library(doParallel)
library(foreach)

cl = makeCluster(detectCores()-2)

@@

# Define biomart object
mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", host = "sep2019.archive.ensembl.org", dataset = "hsapiens_gene_ensembl")

>>>>

library(doParallel)
library(foreach)
library(future)

cl = makeCluster(availableCores()-2)

@@

# Define biomart object
mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", 
                host = "sep2019.archive.ensembl.org", 
                dataset = "hsapiens_gene_ensembl",
                mirror = "uswest")
